Lecture 8: Extensive Form Games with Perfect Information

### 2014-10-08 course-game/session1/ehsan_session1.tex
changes

\documentclass{beamer}
\usepackage[latin1]{inputenc,colortbl}
\usepackage{epsfig}
\usetheme{Frankfurt}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{footline}[page number]
%\newtheorem{definition}{Definition}
\title[Cooperative Decision Making for Communities of Autonomous Web Services]{Cooperative Decision Making for Communities of Autonomous Web Services}
\author{Ehsan Khosrowshahi Asl\\ \vspace{0.2cm} Supervised by: \\Dr. Jamal Bentahar \\Dr. Hadi Otrok}
\institute{Department of Computer Science and Software Engineering\\Concordia University}
\date{December 17, 2013}
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame1 title page %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\titlepage
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame2 outline page %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Presentation Outline}
    \begin{itemize}
     	\itemsep=.5cm
    	\item {\bf Introduction}
    	\item Background and Literature Review
    	\item Proposed Research
    	\item Timeline and Feature Work
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame3 introduction %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
%\section{Motivation}
\subsection{Motivation}
    \begin{frame}{Motivation}
    \begin{itemize}
        \item High reliance on web services created high competition and great business opportunities for online service developers
        \item Community of web services: Clustering similar web services in order to:
        \begin{itemize}
            \item \textbf{Provide better user satisfaction through high availability and responsiveness}.
            \item \textbf{Facilitate Web Service Discovery over Internet}.
            \item \textbf{Maintain high reputation and market share}.
        \end{itemize}
    \end{itemize}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        \includegraphics[width=1.0 \columnwidth]{figures/wsinternet.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}
    \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\subsection{Communities of Web Services}
%    \begin{frame}{Community of Web Services}
%       Communities of Web Services
%       \begin{itemize}
%           \item Ease and improve the process of Web services discovery in an open environment like the Internet
%       	\item Improve service quality, availability and responsiveness
%           \item Maintaining high reputation and market share
%       \end{itemize}

%       \begin{figure}[htbp]
%           \centering
            %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
%           \includegraphics[width=1.0 \columnwidth]{figures/wscommunity2.png}
            %%\includegraphics[scale=0.5]{figure1}
            %\caption{The NetBill payment protocol} \label{figure7}
%       \end{figure}

%   \end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame10 Background and Literature Review %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\subsection{Social commitments in MASs}
    \begin{frame}{Communities of Web Services}
        Communities of Web Services
        \begin{itemize}
            \itemsep=.35cm
        	\item \textbf{Communities of web services operations}
            \begin{itemize}
              \item Community development
              \item Web services attraction and retention
              \item Web service selection
            \end{itemize}                      	      	
        \end{itemize}

        \begin{figure}[htbp]
            \centering
            %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
            \includegraphics[width=1.0 \columnwidth]{figures/wscommunity2.png}
            %%\includegraphics[scale=0.5]{figure1}
            %\caption{The NetBill payment protocol} \label{figure7}
        \end{figure}
    \end{frame}

\begin{frame}{Problems and Research Questions}

\begin{itemize}
    \item \textbf{How can we model the
        community of agent-based services in order to maximize the utility
        of involved users, web services and community organizers?}
        \begin{itemize}
            \item Most of the work on communities of
            services are either user-centric and focus on user satisfaction
            or system-centric and focus on the whole system throughput, performance and utilization.
        \end{itemize}

    \item \textbf{How can we model fair and stable communities as coalitions
        of agent-based web services?}
        \begin{itemize}
            \item All parties involved are self-interest agents and have the right to leave the community if they can improve their income in some other ways.
        \end{itemize}

\end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Continue: Problems and Research Questions}
 \begin{itemize}
   \item \textbf{How can we model and analyze the cooperation
        among the community members in realistic, applicable and practical
        settings?}
        \begin{itemize}
            \item The first issue is about the evaluation of web services that are working together inside communities.
            \item The second issue is about the complexity of cooperative game theory solution concepts.
        \end{itemize}

\end{itemize}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    \begin{frame}{Multi-Agent Systems MASs}
%        \begin{itemize}
%            \itemsep=.35cm
%        	\item Multi-Agent System (MAS).
%            %\item Autonomous agents.
%        	\item Knowledge in MASs.
%            \item Social commitments in MASs.
%        \end{itemize}
%\end{frame}

@@

%    \begin{frame}{Cooperative Game Theory}
%      \begin{itemize}
%         \item Cooperative games are a branch of game theory that models cooperation or collaboration between agents.
%         \begin{itemize}
%            \item Cooperation to perform a set of tasks that requires different expertise.
%            \item Agents do not have enough resource on their own to perform the tasks.
%            \item Examples:
%            \begin{itemize}
%                \item Robots have the ability to move objects in a plant, but multiple robots are required to move a heavy box.
%                \item Transportation domain: agents are trucks, trains, airplanes, ships... a task is a good to be transported.
%            \end{itemize}
%        \end{itemize}
%        \item \textbf{Issues:}
%            \begin{itemize}
%                \item Coalition formation.
%                \item Rewarding members when a task is completed.
%            \end{itemize}
%      \end{itemize}
%    \end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{frame}{Transferable and Non Transferable Utility Games}
%    \begin{itemize}
%        \item \textbf{Games with Transferable Utility (TU games)}
%        \begin{itemize}
%            \item Utility is worth the same for all agents.
%            \item Utility can be {\color{red} compared} or {\color{red} transferred} between agents.
%            \item Irrespective of the division of the coalitional payoff.
%            \begin{itemize}
%                \item In that case members of the coalition enjoy the same total utility.
%            \end{itemize}
%        \end{itemize}
%
%
%        \begin{definition} [Valuation or Characteristic Function]\label{dfn:valuationfunction}
%            A \emph{valuation function v} associates a real number $v(C)$ to any subset $C \subseteq N$, i.e., $v:2^N \rightarrow R$ \\
%            A {\color{blue}\emph{TU game}} is a pair $(N,v)$ where $N$ is a set of agents and where $v$ is a valuation function.
%        \end{definition}
%
%
%
%        \item \textbf{Games with Non Transferable Utility (NTU games)} \\
%            Agents have different preferences over coalitions and rewards. Non-monetary rewards, i.e. item allocation type of problems where items have %different values for different players.
%    \end{itemize}

%\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Some Properties of Valuation Functions}
    $\forall C_1,C_2 \subseteq N | C_1 \bigcap C_2 = \emptyset, i \in N, i \notin C_1$
    \begin{itemize}
        \item {\color{blue} Additive:} $v(C_1 \bigcup C_2) = v(C_1) + v(C_2)$
        \item {\color{blue} Super additive:} $v(C_1 \bigcup C_2) \geq v(C_1) + v(C_2)$ This is satisfied is many applications, or bigger coalitions will not form.
        \item {\color{blue} Weekly super additive:} $v(C_1 \bigcup \{i\}) \geq v(C_1) + v(\{i\})$
        \item {\color{red} Subadditive:} $v(C_1 \bigcup C_2) \leq v(C_1) + v(C_2)$
    \end{itemize}

@@

    \begin{definition} [Shapley Value]\label{dfn:shapleyvalue}
        Given a coalitional game $(N,v)$, the Shapley value of player $i$ is given by: \\
        $\phi_i(N,v) = \sum_{S \subseteq N \backslash \left\{i\right\} } \frac{|S|! (|N|-|S|-1)!}{|N|!} (v(S \cup \left\{i\right\}) - v(S))$
    \end{definition}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Some Properties}
    \begin{itemize}
        \item The core may not always be non-empty.
        \item Shapley value always exists and is unique.
        \item When the valuation function is {\color{blue}superadditive}, the Shapley value is {\color{blue}individually rational}, i.e., it is an imputation.
        \item When the valuation function is {\color{blue}convex}, the Shapley value is also group rational, hence, it is in the {\color{blue}core}.
        \item A convex game has a non-empty core.
        \item Core and Shapley value are combinatorial problems.
        \item There are other well-known solution concepts: The bargaining set, The nucleolus and The nucleolus.
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Proposed Research}
\begin{frame}{Presentation Outline}
    \begin{itemize}
     	\itemsep=.5cm
    	\item Introduction
    	\item Background and Literature Review
    	\item {\bf Proposed Research}
    	\item Timeline and Feature Work
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame16 Proposed Research %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Problem Formulation and Modeling}

\begin{frame}{Problem Formulation and Modeling}
    \begin{itemize}
        \item Communities of web services are robust service providers with well established market share and reputation.
        \item The community is characterized by a request rate $R_C$.
        \item Web services can perform tasks with some throughput rate ($Th_{ws}$).
        \item Web services come with different values of $QoS_{ws}$ for different metrics.
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Task Distribution}
    \begin{itemize}
        \item Our model uses a slightly modified \emph{weighted fair queuing} method for task distribution rather than Contract-Net.
        \item All the input flow is multiplexed amount different web services with weights proportional to their throughput value ($Th_{ws}$).
        \item Queues will happen if $R_C$ is more than summation web services throughput.
        \item Weighted task rate of: $R_C \times \frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ or $Th_{ws}$
    \end{itemize}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        \includegraphics[width=0.8 \columnwidth]{figures/community.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Community Revenue}
    \begin{itemize}
        \item Maximum potential output of a community:
            \begin{equation*}
                PO(C) = \sum_{ws \in C}{(T_{ws} \times QoS_{ws})}
            \end{equation*}
        \item if $\sum_{ws}{Th_{ws}} > R_C$, the community cannot perform at its maximum potential.
        \item Actual output:
            \begin{equation}\label{out_c}
                Out(C) = \left\{
                  \begin{array}{l l}
                    PO(C) & \quad \text{if $\sum_{ws}{Th_{ws}} \leq R_{C}$}\\
                    PO(C) \times \frac{R_{C}}{\sum_{ws}{Th_{ws}}} & \quad \text{if $\sum_{ws}{Th_{ws}} > R_{C}$}
                  \end{array} \right.
            \end{equation}
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Example 1}
    \begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    % if using array.sty, it might be a good idea to tweak the value of
    % \extrarowheight as needed to properly center the text within the cells
    \label{example_1}
    \centering
    \begin{tabular}{c c c c}
    \hline
    $WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
    \hline
    1 & 0.8 & 4 & 3.2\\
    2 & 0.8 & 5 & 4.0\\
    3 & 0.8 & 3 & 2.4\\
    \hline
    \end{tabular}
    \end{table}

    \begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    % if using array.sty, it might be a good idea to tweak the value of
    % \extrarowheight as needed to properly center the text within the cells
    % \caption{Three web services}
    \label{example_1_2}
    \centering
    \begin{tabular}{c c || c c}
    \hline
    Community & Worth & Community & Worth\\
    \hline
    $\left\{1\right\}$ & 3.2 & $\left\{1,2\right\}$ & 7.2\\
    $\left\{2\right\}$ & 4.0 & $\left\{1,3\right\}$ & 5.6\\
    $\left\{3\right\}$ & 2.4 & $\left\{2,3\right\}$ & 6.4\\
    $\left\{1,2,3\right\}$ & 8.0\\
    \hline
    Community $R_C$: 10\\
    \hline
    \end{tabular}
    \end{table}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Example 2}
    \begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    % if using array.sty, it might be a good idea to tweak the value of
    % \extrarowheight as needed to properly center the text within the cells
    \label{example_2}
    \centering
    \begin{tabular}{c c c c}
    \hline
    $WS$ & $QoS_{ws}$ & $Th_{ws}$ & $Th_{ws} \times QoS_{ws}$\\
    \hline
    1 & 0.8 & 5 & 4.0\\
    2 & 0.7 & 6 & 4.2\\
    3 & 0.7 & 4 & 2.8\\
    \hline
    \end{tabular}
    \end{table}

    \begin{table}[!t]
    \renewcommand{\arraystretch}{1.3}
    % if using array.sty, it might be a good idea to tweak the value of
    % \extrarowheight as needed to properly center the text within the cells
    % \caption{Three web services}
    \label{example_2_2}
    \centering
    \begin{tabular}{c c || c c}
    \hline
    Community & Worth & Community & Worth\\
    \hline
    $\left\{1\right\}$ & 4.0 & $\left\{1,2\right\}$ & 7.4\\
    $\left\{2\right\}$ & 4.2 & $\left\{1,3\right\}$ & 6.8\\
    $\left\{3\right\}$ & 2.8 & $\left\{2,3\right\}$ & 7.0\\
    $\left\{1,2,3\right\}$ & 7.3\\
    \hline
    Community $R_C$: 10\\
    \hline
    \end{tabular}
    \end{table}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Example 3}
    \begin{table}[!t]
    \renewcommand{\arraystretch}{0.8}
    % if using array.sty, it might be a good idea to tweak the value of
    % \extrarowheight as needed to properly center the text within the cells
    \label{example_3}
    \centering
    \begin{tabular}{c c c c}
    \hline
    $WS$ & $QoS_{ws}$ & $Th_{ws}$ & $\text{\emph{Input Task Rate}}$\\
    \hline
    1 & 0.8 & 10 & 5\\
    2 & 0.8 & 20 & 5\\
    3 & 0.8 & 30 & 5\\
    \hline
    \end{tabular}
    \end{table}

    \begin{table}[!t]
    \renewcommand{\arraystretch}{0.8}
    % if using array.sty, it might be a good idea to tweak the value of
    % \extrarowheight as needed to properly center the text within the cells
    % \caption{Three web services}
    \label{example_3_2}
    \centering
    \begin{tabular}{c c || c c}
    \hline
    Community & Worth & Community & Worth\\
    \hline
    $\left\{C_{ms_1}\right\}$ & 0 & $\left\{C_{ms_2}\right\}$ & 0\\
    $\left\{C_{ms_1}, ws_1\right\}$ & 8 & $\left\{C_{ms_2}, ws_1\right\}$ & 8\\
    $\left\{C_{ms_1}, ws_2\right\}$ & 16 & $\left\{C_{ms_2}, ws_2\right\}$ & 16\\
    $\left\{C_{ms_1}, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_3\right\}$ & 24\\
    $\left\{C_{ms_1}, ws_1, ws_2\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_2\right\}$ & 24\\
    $\left\{C_{ms_1}, ws_1, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_3\right\}$ & 32\\
    $\left\{C_{ms_1}, ws_2, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_2, ws_3\right\}$ & 32\\
    $\left\{C_{ms_1}, ws_1, ws_2, ws_3\right\}$ & 16 & $\left\{C_{ms_2}, ws_1, ws_2, ws_3\right\}$ & 32\\
    $\left\{C_{ms_1}, C_{ms_2}, ...\right\}$ & 0 & $\left\{ws_1\right\}$ & 6.8\\
    $\left\{ws_2\right\}$ & 4.2 & $\left\{ws_3\right\}$ & 6.8\\
    \hline
    Community $R_{C_1}$: 20 \\ Community $R_{C_2}$: 40\\
    \hline
    \end{tabular}
    \end{table}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame19 Proposed Research
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Web Service Cooperative Games}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Scenario One: Web Services and One Community}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        \includegraphics[width=0.8 \columnwidth]{figures/scenario1.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}

    \begin{itemize}
        \item A typical WS community, where web services can join or leave.
        \item $v(C) = Out(C)$.
        \item Membership decision in made based on throughput and QoS of the web services.
        \item Community master needs to get quality web services to keep community stable, so other web services have no incentive to leave.
    \end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Scenario One: Web Services and One Community}

    \begin{itemize}
        \item Upon receiving membership request the master web service checks if the coalition will be stable having the new member.
        \item If the game is convex, core exists.
        \item If the game is convex, Shapley value is in core.
        \item Convexity Condition:
        \begin{center}
          $v(A \cup B) \geq v(A) + v(B) - v(A \cap B)$ \\
          $\Leftrightarrow$  \\
          $\forall S,T | S \subseteq T \subseteq N \backslash \left\{i\right\}, \forall i \in N,$ \\
          {\color{blue} $v(S \cup \left\{i\right\}) - v(S) \leq v (T \cup \left\{i\right\}) - v(T)$ }
        \end{center}
        \item Depth-1 Convexity Check: $O(n)$
        \item Depth-2 Convexity Check: $O(n^2)$
    \end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Scenario One: Web Services and One Community}

    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        \includegraphics[width=0.92 \columnwidth]{figures/dp.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}

    %\begin{itemize}
    %    \item Approximation of the optimum result for each level, is it possible?
    %\end{itemize}

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Scenario Two: Web Services and Many Communities}
    \begin{itemize}
        \item Based on Coalition Structure theory
        \begin{itemize}
            \item What coalitions to form?
            \item Stability in coalition structure, is a partition of players, where no other partition can provide all agents with better utility.
            \item Social welfare: $\operatorname*{arg\,max}_{CS} v(CS)$ where $v(CS) = \sum_{C \in CS}v(C)$.
        \end{itemize}
        \item Has to be distributed not centralized.
        \item Merge and Split Algorithm {\footnotesize{\color{blue}{(Krzysztof R. Apt and Andreas Witzel)}}}
        \begin{itemize}
            \item Is iterative
            \item Converges to a final partition
        \end{itemize}
    \end{itemize}
    \begin{figure}[htbp]
        \centering
        %\includegraphics[width=12cm, height=8cm]{figures/figure1.eps}
        \includegraphics[width=0.5 \columnwidth]{figures/scenario2.png}
        %%\includegraphics[scale=0.5]{figure1}
        %\caption{The NetBill payment protocol} \label{figure7}
    \end{figure}       	
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame26 Contribution and Research Activities %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Preliminary Results}
\begin{frame}{Preliminary Results}

    \begin{figure}[!t]
    \centering
    %\includegraphics[scale=0.6]{graph1Final+.eps}
    \includegraphics[width=2.1in]{figures/task_done_opt.pdf}
    \includegraphics[width=2.1in]{figures/task_qos_opt.pdf}
    \caption{Part (a): Cumulative number of requests successfully
    done. Part (b): Average QoS of requests performed.}
    \label{performanceall}
    \end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Preliminary Results}
    \begin{figure}[!t]
        \centering
        %\includegraphics[scale=0.6]{graph1Final+.eps}
        \includegraphics[width=3in]{figures/least_core.pdf}
        \caption{Analysis of \emph{$\epsilon$-core} set non-emptiness, for different values of $\epsilon$}. \label{f_leastcore}
    \end{figure}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Preliminary Results}
    \begin{figure}[!t]
        \centering
        %\includegraphics[scale=0.6]{graph1Final+.eps}
        \includegraphics[width=2.1in]{figures/s2_task_done.pdf}
        \includegraphics[width=2.1in]{figures/s2_task_qos.pdf}
        \caption{Part (a): Cumulative number of tasks succesfully done. Part
        (b): Average QoS of tasks performed.} \label{performancemany}
    \end{figure}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Preliminary Results}
    \begin{figure}[!t]
        \centering
        %\includegraphics[scale=0.6]{graph1Final+.eps}
        \includegraphics[width=1.45in]{figures/avg_task_ws_done.pdf}
        \includegraphics[width=1.45in]{figures/avg_qos_ws_done.pdf}
        \includegraphics[width=1.45in]{figures/avg_avail_ws_done.pdf}
        \caption{A comparison between our community model and the high availability community model, on communities of size 4,5,6 only. Part (a): Cumulative number of tasks succesfully done. Part
        (b): Average QoS of tasks performed. (c) Average Community Service Availability} \label{fig_avail_method}
    \end{figure}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame30 outline page
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Milestones}
\begin{frame}{Milestones}
    \begin{itemize}
     	\itemsep=.5cm
    	\item Introduction
    	\item Background and Literature Review
    	\item Proposed Research
    	\item {\bf Timeline and Feature Work}
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Research Activities Goal}
\begin{frame}{Research Activities Goal}
    \begin{enumerate}
        \item Analyzing other cooperative solution concepts such as Kernel
        and Nucleolus where payoff division is guaranteed to exist and may
        have optimal results.

        \item Applying other valuation function in our scenarios using for
        instance Weighted Voting Games (WCG) in order to develop a
        multiple weighted algorithm to find best coalition structures
        satisfying different weights on each community.

        \item Analyzing the impact of Q-learning and reinforcement
        learning on the performance of our model.

        \item Developing a community membership algorithm technique for
        our agents in "incomplete information" settings.

        %\item Developing an open source, Java based Tool, with UI for
        %solving Core and Shapely solution concepts based on different
        %input valuation functions.
    \end{enumerate}
\end{frame}

>>>>

\documentclass{beamer}
\usepackage[latin1]{inputenc,colortbl}
\usepackage{epsfig}
\usetheme{Frankfurt}
\setbeamertemplate{navigation symbols}{}
\setbeamertemplate{footline}[page number]
%\newtheorem{definition}{Definition}
\title[Lecture 8: Extensive Form Games with Perfect Information]{Lecture 8: Extensive Form Games with Perfect Information}
\author{INSE 6441/2 DD\\ \vspace{0.2cm} Applied Game Theory and Mechanism Design \\ Fall 2014}
\institute{Department of Computer Science and Software Engineering\\Concordia University}
\date{Novermber 17, 2014}
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame1 title page %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
\titlepage
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% frame2 outline page %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}{Overview}
    \begin{itemize}
     	\itemsep=.5cm
    	\item {\bf Introduction}
    	\item S2
    	\item S3
    	\item S4
    \end{itemize}
\end{frame}

@@

\begin{frame}{Cooperative Game Theory}
  \begin{itemize}
     \item Cooperative games are a branch of game theory that models cooperation or collaboration between agents.
     \begin{itemize}
        \item Cooperation to perform a set of tasks that requires different expertise.
        \item Agents do not have enough resource on their own to perform the tasks.
        \item Examples:
        \begin{itemize}
            \item Robots have the ability to move objects in a plant, but multiple robots are required to move a heavy box.
            \item Transportation domain: agents are trucks, trains, airplanes, ships... a task is a good to be transported.
        \end{itemize}
    \end{itemize}
    \item \textbf{Issues:}
        \begin{itemize}
            \item Coalition formation.
            \item Rewarding members when a task is completed.
        \end{itemize}
  \end{itemize}
\end{frame}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Transferable and Non Transferable Utility Games}
    \begin{itemize}
        \item \textbf{Games with Transferable Utility (TU games)}
        \begin{itemize}
            \item Utility is worth the same for all agents.
            \item Utility can be {\color{red} compared} or {\color{red} transferred} between agents.
            \item Irrespective of the division of the coalitional payoff.
            \begin{itemize}
                \item In that case members of the coalition enjoy the same total utility.
            \end{itemize}
        \end{itemize}

        \begin{definition} [Valuation or Characteristic Function]\label{dfn:valuationfunction}
            A \emph{valuation function v} associates a real number $v(C)$ to any subset $C \subseteq N$, i.e., $v:2^N \rightarrow R$ \\
            A {\color{blue}\emph{TU game}} is a pair $(N,v)$ where $N$ is a set of agents and where $v$ is a valuation function.
        \end{definition}

        \item \textbf{Games with Non Transferable Utility (NTU games)} \\
            Agents have different preferences over coalitions and rewards. Non-monetary rewards, i.e. item allocation type of problems where items have different values for different players.
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Some Properties of Valuation Functions}
    $\forall C_1,C_2 \subseteq N | C_1 \bigcap C_2 = \emptyset, i \in N, i \notin C_1$
    \begin{itemize}
        \item {\color{blue} Additive:} $v(C_1 \bigcup C_2) = v(C_1) + v(C_2)$
        \item {\color{blue} Super additive:} $v(C_1 \bigcup C_2) \geq v(C_1) + v(C_2)$ This is satisfied is many applications, or bigger coalitions will not form.
        \item {\color{blue} Weekly super additive:} $v(C_1 \bigcup \{i\}) \geq v(C_1) + v(\{i\})$
        \item {\color{red} Subadditive:} $v(C_1 \bigcup C_2) \leq v(C_1) + v(C_2)$
    \end{itemize}

@@

    \begin{definition} [Shapley Value]\label{dfn:shapleyvalue}
        Given a coalitional game $(N,v)$, the Shapley value of player $i$ is given by: \\
        $\phi_i(N,v) = \sum_{S \subseteq N \backslash \left\{i\right\} } \frac{|S|! (|N|-|S|-1)!}{|N|!} (v(S \cup \left\{i\right\}) - v(S))$
    \end{definition}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Some Properties}
    \begin{itemize}
        \item The core may not always be non-empty.
        \item Shapley value always exists and is unique.
        \item When the valuation function is {\color{blue}superadditive}, the Shapley value is {\color{blue}individually rational}, i.e., it is an imputation.
        \item When the valuation function is {\color{blue}convex}, the Shapley value is also group rational, hence, it is in the {\color{blue}core}.
        \item A convex game has a non-empty core.
        \item Core and Shapley value are combinatorial problems.
        \item There are other well-known solution concepts: Bargaining set, nucleolus and kernel.
    \end{itemize}
\end{frame}

@@
